### 2014-03-02 src/paper.Rnw
update

>>>>

<<results='asis'>>=
o <- subset(stats.df[with(stats.df, order(-r.square, -mutant.reduction)),], mutant.reduction != Inf & kind == 'original')
o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'score.multiplier'))
colnames(o.x) <- c('operator', 'r^2', 'm.reduction', 'mcov.mult')
print(xtable(o.x, caption='Original', label='table:try1'), include.rownames=FALSE)
# , sanitize.text.function = function(x){x}, include.rownames=FALSE)
@
<<results='asis'>>=
r <- subset(stats.df[with(stats.df, order(-r.square, -mutant.reduction)),], mutant.reduction != Inf & kind == 'randoop')
r.x <- subset(o, select=c('operator','r.square', 'mutant.reduction', 'score.multiplier'))
colnames(r.x) <- c('operator', 'r^2', 'm.reduction', 'mcov.mult')
print(xtable(r.x, caption='Randoop', label='table:try1'), include.rownames=FALSE)
@
